The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-19 paper.tex
added new figure, completed intro, started to describe Roomba study

In this section we give a brief overview of the studies that we conducted to investigate anthropomorphism. Note that it was not the main purpose of these studies to analyze in detail the effect of different dimensions human-likeness of a robot on the user's perception of and interaction with the robot. Each of these studies

The strong points

@@

>>>>

In this section we give a brief overview of the studies that we conducted to investigate anthropomorphism. Note that it was not the main purpose of these studies to analyze in detail the effect of different dimensions human-likeness of a robot on the user's perception of and interaction with the robot. Each of these studies were motivated also by other research questions, and we encourage the reader to refer to our other main publications about these studies for more details.

@@

We openly explored interactions between human users and a domestic service robot in a 6-months lasting ethnographic study in nine households to which we gave a commercially available vacuum cleaning robot (iRobot's Roomba).\footnote{This study is published in \cite{fink_living_2013}.} Hereafter, we refer to this study as the "Roomba study".

We can report on several findings related to anthropomorphism and the anthropomorphic design of robots. The gathered data for these aspects include qualitative observations, semi-structured interviews, and also quantitative assessments of various aspects of human-robot interaction. The Roomba study is one of very few long-term human-robot interaction studies in the domestic environment.

In the following, we present findings in respect of two aspects:
First, we qualitatively describe what kinds of anthropomorphic interactions between participants and the robot were observed and outline how these interactions evolved over time.
Second, we present people's perception of human-likeness and social capabilities of the robot and how this perception changed over time.

\subsubsection{Anthropomorphic interactions with the robot}

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{roomba-activities.png}
    \caption{This bar chart shows how many of the 9 households carried out different kinds of activities with and related to the robot over a period of 6 months. Activities included using the robot for \texttt{cleaning}, \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, taking a \texttt{photo/video} of the robot, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot, \texttt{hacking} the robot, having a \texttt{conversation} about the robot, making \texttt{adjustments} to the home due to the robot. Participants were asked to report on these activities at 3 time points after the robot was deployed in their home: after 2 weeks, after 2 months, and after 6 months. \hl{(strangely, in the pdf version of this graph the bars were not displayed!)}}

    \label{fig:roomba-activities}
\end{figure}

\subsubsection{Perception of human-like characteristics of the robot}
